DeepTriangle: A Deep Learning Approach to Loss Reserving

### 2019-09-05 manuscript/manuscript.Rmd
typo
hyperparameter details

# Neural network preliminaries

@@

We first encode the sequential predictor with a GRU to obtain a summary of the historical values. We then repeat the output $I-1$ times before passing them to a decoder GRU. The factor $I-1$ is chosen here because for the $I$th accident year, we need to forecast $I-1$ timesteps into the future. Each timestep of the decoded sequence is then concatenated with the company embedding before being passed to two subnetworks, corresponding to the two prediction outputs, of fully connected layers, each of which shares weights across the timesteps.

@@

@@

is used as the activation function for the fully connected layers, including both of the output layers. We remark that this choice of output activation implies we only predict nonnegative cash flows, i.e. no recoveries. This assumption is reasonable for the dataset we use in our experiments, but may be modified to accommodate other use cases.

@@

The loss function for the each output is computed as the average over the forecasted time steps of the mean squared error of the predictions. The losses for the outputs are then averaged to obtain the network loss. Formally, for the sample associated with cell $(i, j)$, we can write the per-sample loss as

>>>>

# Neural network preliminaries [#prelim]

@@

We first encode the sequential predictor with a GRU to obtain a summary encoding of the historical values. We then repeat the output $I-1$ times before passing them to a decoder GRU that outputs its hidden state for each time step. The factor $I-1$ is chosen here because for the $I$th accident year, we need to forecast $I-1$ timesteps into the future. For both the encoder and decoder GRU modules, we use 128 hidden units and a dropout rate of 0.2. Here, dropout refers to the regime where, during training, we randomly set the output of the hidden units to zero with a specified probability, in order to reduce overfitting [@srivastava2014dropout].

@@

Each timestep of the decoded sequence from the GRU decoder is then concatenated with the company embedding output. The concatenated values are then passed to two subnetworks of fully connected layers, each of which shares weights across the timesteps. The two subnetworks correspond to the paid loss and case outstanding predictions, respectively, and each consist of a hidden layer of 64 units with a dropout rate of 0.2, and an output layer of 1 unit to represent a scalar.

@@

is used as the activation function (which we denoted as $g$ in Section \@ref(prelim)) for all fully connected layers, including both of the output layers. We remark that this choice of output activation implies we only predict nonnegative cash flows, i.e. no recoveries. This assumption is reasonable for the dataset we use in our experiments, but may be modified to accommodate other use cases.

@@

The loss function is computed as the average over the forecasted time steps of the mean squared error of the predictions. The losses for the outputs are then averaged to obtain the network loss. Formally, for the sample associated with cell $(i, j)$, we can write the per-sample loss as
